EvoSuite at the SBST 2016 Tool Competition

### 2016-02-21 papers/sbst16/paper_sbst16.tex
added table
luxembourg grant ack
Update tables and paper

\begin{table*}[t]
  \centering
  \caption{\label{table:results}Detailed results of \EVOSUITE on the SBST benchmark classes. Time is expressed in minutes.}
  %\scriptsize
\resizebox{0.9\textwidth}{!}{  
  \begin{tabular}{l rrrrrr} \toprule
Class &  JUnit Files &   Generation Time & Execution Time   & \% Line Coverage & \% Branch Coverage & \% Mutation Score \\  
\midrule
%\input{results.tex}
\midrule
%Average & & 6.19 & 0.03 & 55.36 & 47.19 & 41.02\\
\bottomrule
  \end{tabular}
}
\end{table*}

The results of \EVOSUITE on the benchmark classes are listed in
Table~\ref{table:results}. On average, \EVOSUITE achieved []\% line
coverage, []\% branch coverage\footnote{Using Cobertura's definition
  of branch coverage, which only counts conditional statements, not
  edges in the CFG.}, and []\% mutation score.

\subsection{Issues Encountered}

Following recent experiments on
Defects4J~\cite{shamshiri2015automatically} that revealed general
issues in unit test generation, \EVOSUITE now includes assertions on
the source of exceptions, similar to commercial tools like Agitar
One~\cite{agitarone}. However, there were several instances in the
competition where these assertions lead to flaky tests. For example,
the following is an excerpt from a test for the Defects4J bug Lang-41,
generated by \EVOSUITE:

@@

@@

With an overall score of [], \EVOSUITE achieved the []
 score of all tools in the competition.

@@

Many thanks to all the contributors to \EVOSUITE.

>>>>

% \begin{table*}[t]
%   \centering
%   \caption{\label{table:results}Detailed results of \EVOSUITE on the SBST benchmark classes.}
% \resizebox{0.9\textwidth}{!}{  
% \input{mainTable.tex}
% }	
% \end{table*}

\begin{table*}[t]
  \centering
  \caption{\label{table:coverage_results}Detailed coverage results of \EVOSUITE on the SBST benchmark classes.}
\resizebox{0.9\textwidth}{!}{  
\input{coverageTable.tex}
}
\end{table*}

\begin{table*}[t]
  \centering
  \caption{\label{table:fault_results}Detailed fault detection results of \EVOSUITE on the SBST benchmark classes.}
\resizebox{0.9\textwidth}{!}{  
\input{faultTable.tex}
}	
\end{table*}

The coverage results (line coverage and branch coverage) achieved by
\EVOSUITE on the benchmark classes are listed in
Table~\ref{table:coverage_results}. Coverage is generally in the
expected range, with clear increases for higher time budgets. Coverage
on several of the benchmarks from Closure is low, which matches
previous findings~\cite{shamshiri2015automatically}.

Results in terms of mutation scores and fault detection ratio (i.e.,
how many of the runs had at least one failing test on the
corresponding bug) are showing in
Table~\ref{table:fault_results}. Again the Closure results are
generally worse than those of other projects, both in terms of
mutation score and ratio of fault detection.

On average, \EVOSUITE generated 0.14 flaky tests per run, a value that
is significantly lower than that of any of the competing tools. This
is due to extensive efforts to isolate \EVOSUITE tests from the
execution environment~\cite{arcuri2014automated}. A few of these flaky
tests were introduced by recent changes to \EVOSUITE following
experiments on Defects4J~\cite{shamshiri2015automatically}: \EVOSUITE
now includes assertions on the source of exceptions, similar to
commercial tools like Agitar One~\cite{agitarone}. Unfortunately,
there were several instances in the competition where these assertions
lead to flaky tests. For example, the following is an excerpt from a
test for the Defects4J bug Lang-41, generated by \EVOSUITE:

@@

There are 15 runs in total where \EVOSUITE did not produce any test
suites; these are only for higher time budgets (240s, 480s). The
majority of these runs are due to \EVOSUITE not terminating before the
hard timeout of the competition infrastructure. This may happen, for
example, when test execution on the class under test takes long (e.g.,
timeouts), and when resetting the static state of the classes under
test takes a long time. However, this number is still lower than the
number of erroneous runs compared to other tools, and in the remaining
1617 runs of the competition \EVOSUITE terminated in time and produced
at least two tests. In 13 of these, \EVOSUITE produced a test suite
with a compile error.

@@

With an overall score of 1126.7, \EVOSUITE achieved the highest score
of all tools in the competition.

@@

Many thanks to all the contributors to \EVOSUITE.
This project has been funded by 
%the EPSRC project ``EXOGEN'' (EP/K030353/1), a Google Focused Research Award on ``Test
%Amplification'', and by 
the National Research Fund, Luxembourg (FNR/P10/03).
